\section{Conclusion}

In this study, we systematically explored the growth, stability, chemical transformations, and lithographic performance of hybrid organic–inorganic films deposited via molecular layer deposition (MLD), focusing specifically on alucone and zincone networks formed with a range of bifunctional organic diols. Comprehensive evaluation of film deposition, environmental stability, chemical robustness, and developer compatibility identified alucone films based on 1,4-butynediol (BTY) and trihydroxybenzene (THB) as the most promising candidates for advanced lithographic applications.

Key findings include the critical role of UV-induced crosslinking in substantially enhancing the stability and chemical resistance of alucone networks. FTIR spectroscopy demonstrated clear evidence of photochemically initiated crosslinking reactions, resulting in increased network densification, reduction of residual hydroxyl groups, and enhanced conjugation within the hybrid structure. Complementary XPS analyses confirmed that UV-induced crosslinking effectively stabilizes Al–O–C linkages, substantially inhibiting hydrolytic degradation and preserving the organic framework integrity upon exposure to aqueous environments.

Developer compatibility tests established that dilute hydrochloric acid provides excellent chemical contrast between UV-treated and as-deposited alucone films, making it an ideal choice for subsequent lithographic development processes. Electron-beam lithography (EBL) studies further revealed significant improvements in sensitivity, resolution, and contrast for UV-stabilized alucones. Specifically, UV-treated BTY-based alucone films exhibited exceptional negative-tone lithographic behavior, enabling reproducible sub-50~nm feature patterning at substantially reduced electron-beam doses compared to conventional inorganic resist systems.

The detailed mechanistic insights obtained from combined FTIR and XPS analyses established that UV-induced organic crosslinking is the primary driver behind the observed stabilization and lithographic performance improvements. Unlike previously studied alucone systems relying solely on inorganic densification, the organic crosslinking approach demonstrated here provides superior sensitivity, pattern fidelity, and overall lithographic performance.

Collectively, these results highlight the substantial potential of UV-stabilized alucone films as advanced hybrid resists for high-resolution, low-dose electron-beam lithography and possibly extreme ultraviolet (EUV) lithography applications. The clear relationship between chemical composition, UV-induced network densification, environmental robustness, and lithographic performance demonstrated in this work provides valuable guidelines for designing next-generation hybrid materials tailored specifically for advanced nanoscale patterning technologies.
